---
title: "results"
output: html_document
date: "2025-03-20"
---

```{r setup}
library(metafor)  # Load the metafor package
library(synthdid)
library(data.table)
library(tidyverse)
library(dplyr)
library(lubridate)
library(ggplot2)
library(zoo)
library(openxlsx)
library(lme4)
library(pheatmap)
library(circlize)
library(gridExtra)
library(patchwork)
library(forestplot)
library(RColorBrewer)
library(stringr)
options(warn=-1)
```


  
  
```{r table 1 WeCount}
colnames(dataWC)


label(dataWC$abortion_rate)   <- "Abortion Rate"
label(dataWC$repf_population)   <- "Reproductive Age Women"

units(dataWC$abortion_rate)   <- "1000 women age 15-44"
units

table1(~ Abortions + abortion_rate + repf_population | classification_3
                   , data = dataWC, render="Mean (CV%)<br/>Median [Min, Max]",  transpose = TRUE)

table1(~ Abortions + abortion_rate + repf_population | classification_6, data = dataWC)
```

```{r big forrest plot w ggplot}
chapt1 <- read.xlsx("data/final_results.xlsx")
unique(chapt1$type)
chapt1$estimate <- as.numeric(chapt1$estimate)

chapt1$type <- factor(chapt1$type, levels = rev(c("Total Ban","Bans", "6 Week" , "12 Week" , "15 Week", "18 Week",   "20 Week" , "7-20 Weeks", "22 Week"  , "24 Week"  , "Viability", "No Bans", "No Limit","Spillover", "Not Protected", "Expanded Access", "Protected",  "Hostile",  "Illegal", "Friendly", "Not Friendly")))

chapt1$name <- factor(chapt1$name, levels = chapt1$name[order(chapt1$type)])
chapt1$name <- reorder(chapt1$name, chapt1$method)

chapt1_attitude <- chapt1 %>%
  filter(grepl("Attitude|FNF", as.character(model), ignore.case = TRUE))

chapt1 <- chapt1 %>%
  filter(!grepl("Attitude|FNF", as.character(model), ignore.case = TRUE))

#ALL ESTIMATES 
ggplot(chapt1, aes(x = estimate, 
                   y = reorder(name, method),  # Reorder based on 'type' factor levels
                   xmin = lower_ci, 
                   xmax = upper_ci, 
                   color = type)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "black") +  # Vertical line at 0
  geom_point(size = 1.5) +  # Plot the point estimate
  geom_errorbarh(height = 0.5) +
  geom_text(aes(label = paste(round(estimate, 2), 
                              "(", round(lower_ci, 2), ",", round(upper_ci, 2), ")")),
            hjust = 0.7, vjust = -.9, size = 2.5, color = "black") + 
  labs(title = "All Estimates on Policy",
       x = "Estimate (with 95% CI)",
       y = "Model",
       color = "Type") +
  theme_minimal() +  # Use minimal theme
  theme(
        plot.title = element_text(hjust = 0.5),  # Center the title
        axis.text.y = element_text(size = 7, hjust = 0, color = "black"),    # Adjust the y-axis labels' font size
        panel.grid.minor.x = element_blank(),  # Add grid lines at minor x-axis ticks
        panel.grid.major.y = element_line(color = "gray85", size = 0.5),  # Darker major grid lines
        panel.border = element_blank(), 
        legend.text = element_text(size = 7)  # Set smaller font size for legend labels
      ) +  # Remove panel border
  guides(color = guide_legend(ncol = 1, byrow = TRUE)) +  # Wrap the legend into 2 columns 
  scale_x_continuous(labels = label_number(), breaks = pretty_breaks(n = 10), 
                     expand = expansion(mult = 0.1)) +  # Adds padding around CI limits
  scale_y_discrete(labels = function(x) str_wrap(x, width = 50)) +  
  coord_cartesian(clip = "off")  # Ensures no clipping of error bars or points

```

```{r}
#ATTITUDE

ggplot(chapt1_attitude, aes(x = estimate, 
                   y = reorder(name, type),  # Reorder based on 'type' factor levels
                   xmin = lower_ci, 
                   xmax = upper_ci, 
                   color = type)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "black") +  # Vertical line at 0
  geom_point(size = 1.5) +  # Plot the point estimate
  geom_errorbarh(height = 0.5) +  # Add horizontal error bars for confidence intervals
    geom_text(aes(label = paste(round(estimate, 2), 
                              "(", round(lower_ci, 2), ",", round(upper_ci, 2), ")")),
             vjust = -1, size = 2.5, color = "black") + 
  labs(title = "All Estimates on Attitude",
       x = "Estimate (with 95% CI)",
       y = "Model",
       color = "Type") +
  theme_minimal() +  # Use minimal theme
  theme(
        plot.title = element_text(hjust = 0.5),  # Center the title
        axis.text.y = element_text(size = 8, hjust = 0, color = "black"),    # Adjust the y-axis labels' font size
        panel.grid.major.x = element_line(),    # Remove vertical grid lines (major grid lines on x-axis)
        panel.grid.minor.x = element_blank(),  # Add grid lines at minor x-axis ticks
        panel.grid.minor.y = element_line(),     # Keep minor horizontal grid lines (if any)
        panel.border = element_blank(), 
        legend.text = element_text(size = 8)  # Set smaller font size for legend labels
      ) +  # Remove panel border
  guides(color = guide_legend(ncol = 1, byrow = TRUE)) +  # Wrap the legend into 2 columns 
  scale_x_continuous(labels = label_number(), breaks = pretty_breaks(n = 8), 
                     expand = expansion(mult = 0.1)) +  # Adds padding around CI limits
  scale_y_discrete(labels = function(x) str_wrap(x, width = 35)) +  
  coord_cartesian(clip = "off")  # Ensures no clipping of error bars or points
```

```{r individual plots}

# Read the data
chapt1 <- read.xlsx("data/final_results.xlsx")

# Factorize the 'type' and 'name' columns
chapt1$type <- factor(chapt1$type, levels = rev(c("Total Ban","Bans", "6-20 Week", "6 Week", "12 Week", "15 Week", "18 Week", "20 Week", "22 Week", "24 Week", "Viability", "No Limit","Spillover")))

chapt1$method <- as.factor(chapt1$method)
chapt1$estimate <- as.numeric(chapt1$estimate)

# Split data into groups
total_bans <- chapt1 %>% filter(type == "Total Ban")
bans <- chapt1 %>% filter(type == "Bans")
week_groups <- chapt1 %>% filter(grepl("Week", type))  # Any type with "Week"
viability_no_limit <- chapt1 %>% filter(type == "Viability" | type == "No Limit")
spillover <- chapt1 %>% filter(type == "Spillover")

# Function to create a ggplot for the forest plot
create_forest_plot <- function(data, title, label_size, legend_size, width) {
  # Reorder y-axis labels based on the 'method' column
  data$name <- factor(data$name, levels = data$name[order(data$method)])

  ggplot(data, aes(x = estimate, 
                   y = reorder(name, method),  # Reorder based on 'type' factor levels
                   xmin = lower_ci, 
                   xmax = upper_ci, 
                   color = method)) +
    geom_vline(xintercept = 0, linetype = "dashed", color = "black") +  # Vertical line at 0
    geom_point(size = 2) +  # Plot the point estimate
    geom_errorbarh(height = 0.5) +  # Add horizontal error bars for confidence intervals
    labs(
      title = paste(title, "Estimates"),  # Concatenate the title with "Estimates"
      x = "Estimate (with 95% CI)",       # X-axis label
      y = "Model",                        # Y-axis label
      color = "Method"                    # Legend label for color
    ) +
    theme_minimal() +  # Use minimal theme
    theme(
          plot.title = element_text(hjust = 0.5),  # Center the title
          axis.text.y = element_text(size = label_size, hjust = 0),    # Adjust the y-axis labels' font size
          panel.grid.minor.x = element_line(),    # Remove vertical grid lines (minor grid lines on x-axis)
          panel.grid.major.y = element_line(),     # Keep horizontal grid lines (major grid lines on y-axis)
          panel.grid.minor.y = element_line(),  # Remove rotation of y-axis labels if needed
      legend.key.size = unit(0.5, "cm"),       # Set legend key size (smaller keys)
      legend.text = element_text(size = legend_size),    # Set legend text size (smaller text)
      legend.title = element_text(size = 10)   # Set legend title size (optional)
          )   +
    scale_y_discrete(labels = function(x) str_wrap(x, width = width))  # Wrap the y-axis labels
}

# Create individual plots
plot_total_bans <- create_forest_plot(total_bans, "Total Ban", 9, 8, 40)
plot_bans <- create_forest_plot(bans, "Bans", 10, 9, 25)
plot_spillover <- create_forest_plot(spillover, "Spillover", 10, 9, 20)

print(plot_total_bans)
print(plot_bans)
print(plot_spillover)
```

```{r weeks}
week_groups$name <- factor(week_groups$name, levels = week_groups$name[order(week_groups$type)])
viability_no_limit$name <- factor(viability_no_limit$name, levels = viability_no_limit$name[order(viability_no_limit$type)])

gest <- rbind(week_groups, viability_no_limit)

gest$type <- factor(gest$type, levels = rev(c("Total Ban","Bans", "6 Week", "12 Week", "15 Week", "18 Week", "20 Week", "6-20 Week","22 Week", "24 Week", "Viability", "No Limit","Spillover")))

gest$name <- factor(gest$name, levels = gest$name[order(gest$type)])


ggplot(gest, aes(x = estimate, 
                   y = reorder(name, type),  # Reorder based on 'type' factor levels
                   xmin = lower_ci, 
                   xmax = upper_ci, 
                   color = type)) +
    geom_vline(xintercept = 0, linetype = "dashed", color = "black") +  # Vertical line at 0
    geom_point(size = 2) +  # Plot the point estimate
    geom_errorbarh(height = 0.5) +
 geom_text(aes(label = paste(round(estimate, 2))), 
            vjust = -1, size = 3, color = "black") +  # Add text annotations for the estimates
# Add horizontal error bars for confidence intervals
    labs(
      title = "Specific Ban Estimates",  # Concatenate the title with "Estimates"
      x = "Estimate (with 95% CI)",       # X-axis label
      y = "Model",                        # Y-axis label
      color = "Week"                    # Legend label for color
    ) +
    theme_minimal() +  # Use minimal theme
    theme(
          plot.title = element_text(hjust = 0.5),  # Center the title
          axis.text.y = element_text(size = 8, hjust = 0, color = "black"),    # Adjust the y-axis labels' font size
          panel.grid.minor.x = element_blank(),    # Remove vertical grid lines (minor grid lines on x-axis)
          panel.grid.major.y = element_line(),     # Keep horizontal grid lines (major grid lines on y-axis)
          panel.grid.minor.y = element_line(),  # Remove rotation of y-axis labels if needed
      legend.key.size = unit(0.5, "cm"),       # Set legend key size (smaller keys)
      legend.text = element_text(size = 8),    # Set legend text size (smaller text)
      legend.title = element_text(size = 10)   # Set legend title size (optional)
          )   +
    scale_y_discrete(labels = function(x) str_wrap(x, width = 60)) + # Wrap the y-axis labels
  scale_x_continuous(labels = scales::label_number(), breaks = scales::pretty_breaks(n = 10))  # More x-axis labels


ggplot(viability_no_limit, aes(x = estimate, 
                   y = reorder(name, type),  # Reorder based on 'type' factor levels
                   xmin = lower_ci, 
                   xmax = upper_ci, 
                   color = type)) +
    geom_vline(xintercept = 0, linetype = "dashed", color = "black") +  # Vertical line at 0
    geom_point(size = 2) +  # Plot the point estimate
    geom_errorbarh(height = 0.5) +  # Add horizontal error bars for confidence intervals
    labs(
      title = "Viability and No Limit Estimates",  # Concatenate the title with "Estimates"
      x = "Estimate (with 95% CI)",       # X-axis label
      y = "Model",                        # Y-axis label
      color = "Week"                    # Legend label for color
    ) +
    theme_minimal() +  # Use minimal theme
    theme(
          plot.title = element_text(hjust = 0.5),  # Center the title
          axis.text.y = element_text(size = 9, hjust = 0),    # Adjust the y-axis labels' font size
          panel.grid.minor.x = element_blank(),    # Remove vertical grid lines (minor grid lines on x-axis)
          panel.grid.major.y = element_line(),     # Keep horizontal grid lines (major grid lines on y-axis)
          panel.grid.minor.y = element_line(),  # Remove rotation of y-axis labels if needed
      legend.key.size = unit(0.5, "cm"),       # Set legend key size (smaller keys)
      legend.text = element_text(size = 10),    # Set legend text size (smaller text)
      legend.title = element_text(size = 10)   # Set legend title size (optional)
          )   +
    scale_y_discrete(labels = function(x) str_wrap(x, width = 30))  # Wrap the y-axis labels
```


```{r Metanalaysis for Total Bans}
# Calculate the standard error from the confidence intervals
total_bans$se <- (total_bans$upper_ci - total_bans$lower_ci) / (2 * qnorm(0.975))

total_bans <- total_bans %>% 
  mutate(rank = case_when(
    grepl("ME", method) ~ 2,  # Weight 1 if 'method' includes "ME"
    grepl("SDID", method) ~ 1, # Weight 2 if 'method' includes "SDID"
    grepl("DID", method) ~ 3,  # Weight 3 if 'method' includes "DID"
    TRUE ~ NA_real_  # If no match, assign NA (or you could set another value)
  ))

# Run the meta-analysis using the `rma` function from the `metafor` package
meta_analysis_tbans <- rma(yi = estimate,  # Effect size estimates
                     sei = se,      # Standard error for each estimate
                     data = total_bans,
                     weights = 1/rank,
                     method = "REML")  # Restricted maximum likelihood method

# Summary of the meta-analysis
summary(meta_analysis_tbans)

a <- forest(meta_analysis_tbans,
       slab = total_bans$name,      # Study labels
       xlab = "Change in Abortion Rate",
       refline = 0,            # Reference line at 1
       main = "Total Ban Forest Plot Weighted by Method", 
       cex=0.75)
```



```{r meta analysis for spillover}
spillover$se <- (spillover$upper_ci - spillover$lower_ci) / (2 * qnorm(0.975))

spillover <- spillover %>% 
  mutate(name = paste(data, method))

spillover <- spillover %>% 
  mutate(rank = case_when(
    grepl("ME", method) ~ 2,  # Weight 1 if 'method' includes "ME"
    grepl("SDID", method) ~ 1, # Weight 2 if 'method' includes "SDID"
    grepl("DID", method) ~ 3,  # Weight 3 if 'method' includes "DID"
    TRUE ~ NA_real_  # If no match, assign NA (or you could set another value)
  ))

# Run the meta-analysis using the `rma` function from the `metafor` package
meta_analysis_spillover <- rma(yi = estimate,  # Effect size estimates
                     sei = se,      # Standard error for each estimate
                     data = spillover,
                     weights = 1/rank,
                     method = "REML")  # Restricted maximum likelihood method

# Summary of the meta-analysis
summary(meta_analysis_spillover)

b <- forest(meta_analysis_spillover,
       slab = spillover$name,      # Study labels
       xlab = "Change in Abortion Rate",
       refline = 0,            # Reference line at 1
       main = "Spillover Forest Plot Weighted by Method", 
       cex=0.75)
```

```{r metaanalysis for week 6}
week6 <- week_groups %>%
  filter(type == "6 Week")

week6$se <- (week6$upper_ci - week6$lower_ci) / (2 * qnorm(0.975))

week6 <- week6 %>% 
  mutate(name = sub(" 6 Week$", "", name))

week6 <- week6 %>% 
  mutate(rank = case_when(
    grepl("ME", method) ~ 2,  # Weight 1 if 'method' includes "ME"
    grepl("SDID", method) ~ 1, # Weight 2 if 'method' includes "SDID"
    grepl("DID", method) ~ 3,  # Weight 3 if 'method' includes "DID"
    TRUE ~ NA_real_  # If no match, assign NA (or you could set another value)
  ))

# Run the meta-analysis using the `rma` function from the `metafor` package
meta_analysis_6 <- rma(yi = estimate,  # Effect size estimates
                     sei = se,      # Standard error for each estimate
                     data = week6,
                     weights = 1/rank,
                     method = "REML")  # Restricted maximum likelihood method

# Summary of the meta-analysis
summary(meta_analysis_6)

c <- forest(meta_analysis_6,
       slab = week6$name,      # Study labels
       xlab = "Change in Abortion Rate",
       refline = 0,            # Reference line at 1
       main = "6 Week Ban Forest Plot Weighted by Method", 
       cex=0.75)
```

```{r meta analysis bans}
bans$se <- (bans$upper_ci - bans$lower_ci) / (2 * qnorm(0.975))

bans <- bans %>% 
  mutate(name = sub(" Bans$", "", name)) %>% 
  filter(name != "Guttmacher SDID Pre-Viability")

bans <- bans %>% 
  mutate(rank = case_when(
    grepl("ME", method) ~ 2,  # Weight 1 if 'method' includes "ME"
    grepl("SDID", method) ~ 1, # Weight 2 if 'method' includes "SDID"
    grepl("DID", method) ~ 3,  # Weight 3 if 'method' includes "DID"
    TRUE ~ NA_real_  # If no match, assign NA (or you could set another value)
  ))

# Run the meta-analysis using the `rma` function from the `metafor` package
meta_analysis_bans <- rma(yi = estimate,  # Effect size estimates
                     sei = se,      # Standard error for each estimate
                     data = bans,
                     weights = 1/rank,
                     method = "REML")  # Restricted maximum likelihood method

# Summary of the meta-analysis
summary(meta_analysis_bans)

forest(meta_analysis_bans,
       slab = bans$name,      # Study labels
       xlab = "Change in Abortion Rate",
       refline = NA,            # Reference line at 1
       main = "Ban (General) Forest Plot Weighted by Method", 
       cex=0.75)

```


```{r pooled variance}
poolv <- function(data, estimate, bigse){
data <- data %>% 
  mutate(var = se^2)

agv <- sum(data$var/nrow(data))
agse <- sqrt((agv + (bigse)^2)/2)

lo <- estimate - agse*qnorm(0.95)
up <- estimate + agse*qnorm(0.95)


print(paste("pooled se:",agse))
print(paste("estimate:",estimate))
print(paste("lower:",lo))
print(paste("upper:",up))

}

#just take all the variances of the individual "studies" and then divide by the number of studies 
summary(meta_analysis_tbans)
summary(meta_analysis_6)
summary(meta_analysis_bans)
summary(meta_analysis_spillover)


poolv(total_bans,  -0.5817  , 0.0892)
poolv(week6,  -0.2963, 0.0843)
poolv(bans,  -0.5629, 0.1037)
poolv(spillover, 0.2721, 0.1010) 
```

```{r}
# Initialize an empty data frame to store results
result_df <- data.frame(
  Input_Name = character(),
  Estimate = numeric(),
  Lower = numeric(),
  Upper = numeric(),
  stringsAsFactors = FALSE
)

# Modified poolv function
poolv <- function(data, input_name, estimate, bigse) {
  # Calculate variance for each observation and pooled standard error
  data <- data %>% mutate(var = se^2)
  agv <- sum(data$var / nrow(data))
  agse <- sqrt(agv + (bigse)^2)
  
  # Calculate the 95% Confidence Interval
  lo <- estimate - agse * qnorm(0.95)
  up <- estimate + agse * qnorm(0.95)
  
  # Print results (can also be captured or logged if needed)
  print(paste("pooled se:", agse))
  print(paste("estimate:", estimate))
  print(paste("lower:", lo))
  print(paste("upper:", up))
  
  # Round the values to 3 digits
  estimate_rounded <- round(estimate, 3)
  lower_rounded <- round(lo, 3)
  upper_rounded <- round(up, 3)
  
  # Create a new row for the result dataframe
  new_row <- data.frame(
    Input_Name = input_name,
    Estimate = estimate_rounded,
    Lower = lower_rounded,
    Upper = upper_rounded,
    stringsAsFactors = FALSE
  )
  
  # Append the new row to the result_df dataframe
  assign("result_df", rbind(result_df, new_row), envir = .GlobalEnv)
}

# Example usage of the modified poolv function with the 'data' and estimates
# Assuming 'data' is your dataframe with the necessary columns (se and other data)
# You would call it as follows:

# Example data frame (replace with actual data)
data <- data.frame(se = c(0.08, 0.12, 0.10, 0.09))  # Example standard errors

# Call poolv function
poolv(data, "total_bans", -0.5817, 0.0892)
poolv(data, "week6", -0.2963, 0.0843)
poolv(data, "bans", -0.5629, 0.1037)
poolv(data, "spillover", 0.2721, 0.1010)

# View the final result dataframe
print(result_df)
```


```{r interpretations}

statesban <- unique(dataWC$State[dataWC$classification_6 == "ban"])
length(statesban)

statesbang <- unique(dataGMCSDIDbans$State[dataGMCSDIDbans$Treated == 1])
length(statesbang)

setdiff(statesbang, statesban)

total_ban_states_23 <- unique(dataWC$State[dataWC$classification_3 == "total_ban" & dataWC$Year == 2023])
total_ban_states_22
length(total_ban_states_23)

# Identify states with a total ban in 2023
total_ban_states_23 <- unique(dataWC$State[dataWC$classification_3 == "total_ban" & dataWC$Year == 2023])

# Filter data for these states when classification_3 was "predobbs"
predobbs_data <- dataWC[dataWC$State %in% total_ban_states_23 & dataWC$classification_3 == "preDobbs", ]

# Calculate the average abortion rate
average_abortion_rate <- mean(predobbs_data$abortion_rate, na.rm = TRUE)

# Print the result
average_abortion_rate


week6states <- unique(dataWC$State[dataWC$classification_3 == "six_week"])
states_with_some_bans 

spilloverstates <- unique(dataWecount5$State[dataWecount5$classification_5 == "spillover_guttmacher"])

spilloverstates

spilloverstates2 <- unique(dataWC$State[dataWC$classification_5 == "spillover_guttmacher"])

spilloverstates2

model_data <- data.frame(
  Model = c("Aggregate Total Ban", "Aggregate 6 Week", "Aggregate Bans", "Aggregate Spillover at 95%", "Aggregate Spillover at 90%"),
  Estimate = c(-0.6138, -0.3195, -0.6579, 0.1868, 0.1868),
  Lower_CI = c(-0.875852164057328, -0.415119275423007, -0.882175214818891, -0.0081512604906511, 0.0231917447329729),
  Upper_CI = c(-0.351747835942672, -0.223880724576993, -0.433624785181109, 0.381751260490651, 0.350408255267027),
  Number_States = c(length(total_ban_states), length(week6states), length(states_with_some_bans), length(spilloverstates), length(spilloverstates))
)

bigpop_2023 <- bigpop %>% 
  filter(Year == 2023)

aggregate_population <- data.frame(
  Model = c("Aggregate Total Ban", "Aggregate 6 Week", "Aggregate Bans", "Aggregate Spillover at 95%", "Aggregate Spillover at 90%"),
  Total_repFPopulation = c(
    sum(bigpop_2023$repf[bigpop_2023$State %in% total_ban_states_23]),
    sum(bigpop_2023$repf[bigpop_2023$State %in% week6states]),
    sum(bigpop_2023$repf[bigpop_2023$State %in% statesban]), 
    sum(bigpop_2023$repf[bigpop_2023$State %in% spilloverstates2]),
      sum(bigpop_2023$repf[bigpop_2023$State %in% spilloverstates])
  )
)

total_ban_abortion_rate_2023 <- sum(
  CombinedGuttmacherCorrect$abortion_rate[
    CombinedGuttmacherCorrect$State %in% total_ban_states & year(CombinedGuttmacherCorrect$Time) == 2023
  ]
)

total_ban_abortion_rate_2023

total_ban_abortion_rate_2019 <- sum(
  CombinedGuttmacherCorrect$abortion_rate[
    CombinedGuttmacherCorrect$State %in% total_ban_states & year(CombinedGuttmacherCorrect$Time) == 2019
  ]
)

total_ban_abortion_rate_2019

total_ban_abortion_count_2022 <- sum(
  dataWecountRateCorrect$Abortions[
    dataWecountRateCorrect$State %in% total_ban_states & year(dataWecountRateCorrect$Time) == 2022])

total_ban_abortion_count_2022

results <- left_join(model_data, aggregate_population)

results <- results %>% 
  mutate(
    change_aggregate_rate = Estimate * 12,
    aggregate_rate_lo_CI = Lower_CI * 12, 
    aggregate_rate_up_CI = Upper_CI * 12,
    change_aggregate_count_annual = (Estimate/1000) * Total_repFPopulation * 12,
    aggregate_lo_CI = (Lower_CI/1000) * Total_repFPopulation * 12, 
    aggregate_up_CI = (Upper_CI/1000) * Total_repFPopulation * 12
  )
results


df_transposed <- t(results)

resultssimp <- results %>% 
  select(-Number_States, -Total_repFPopulation)

resultssimp <- resultssimp %>% 
    mutate(Estimate_Rate = paste(Estimate, " (", round(Lower_CI, 4), ", ", round(Upper_CI, 4), ")", sep = "")) %>% 
    mutate(Estimate_Rate_agg = paste(change_aggregate_rate, " (", round(aggregate_rate_lo_CI, 4), ", ", round(aggregate_rate_up_CI, 4), ")", sep = "")) %>% 
    mutate(Estimate_Count = paste(round(change_aggregate_count_annual, -3), " (", round(aggregate_lo_CI, -3), ", ", round(aggregate_up_CI,-3), ")", sep = ""))

```

#average all the CI bounds, estimate the variance from the variance estimates (natural variability within estimates) 
current CI is measuring BETWEEN estimate variances. we also want WITHIN different estimate variances. should be able to just average them (on variance, then transform into SE)
just take all the variances of the individual "studies" and then divide by the number of studies 
pooled variance 
#assumes all variance estimates have same degrees of freedom (which is not the case bc theyre different, but not that different)

#How to do confint for normal transformations 
#estimate with CI, just transform the CI the exact same way you transform the estimates 
#problem: because the estimaets are same model on basically same dataset, violates the independence problem, so the margin of error should be much higher 

```{r interpetations models with interactions}
Sigma <- vcov(model2)
beta <- summary(model2)$coef[, "Estimate"]
beta
contrast <- c(rep(0,9), 1, -1) #which terms I want 

p <- as.numeric(t(beta)%*%contrast) #point_estimate

v <- as.numeric(t(contrast)%*%Sigma%*%contrast) #variance 

p + sqrt(v)*1.96
p - sqrt(v)*1.96


interp <- function(model, contrast){
Sigma <- vcov(model)
beta <- summary(model)$coef[, "Estimate"]
beta

p <- as.numeric(t(beta)%*%contrast) #point_estimate

v <- as.numeric(t(contrast)%*%Sigma%*%contrast) #variance 

upper <- p + sqrt(v)*qnorm(0.975)
lower <- p - sqrt(v)*qnorm(0.975)
print(paste("estimate:",p))
print(paste("lower:",lower))
print(paste("upwper:",upper))
}

interp(model2, c(rep(0,9), 1, -1))

interp(model5, c(0,0, -1, 0, 1))
interp(model5, c(0,0, -1, 1, 0))
interp(model5g, c(0,0, -1, 0, 1))
interp(model5g, c(0,0, -1, 1, 0))
interp(model5g, c(0,0, -1, 0, 1))
interp(model5g, c(0,0, -1, 1, 0))

summary(model5)
confint(model5)
```

```{r final}

final_results <- chapt1 %>% 
  mutate(
    annual_estimate = estimate * 12,
    annual_estimate_lo = lower_ci * 12, 
    annual_estimate_up = upper_ci * 12
) 

df_transposed <- t(results)

resultssimp <- results %>% 
  select(-Number_States, -Total_repFPopulation)

resultssimp <- resultssimp %>% 
    mutate(Estimate_Rate = paste(Estimate, " (", round(Lower_CI, 4), ", ", round(Upper_CI, 4), ")", sep = "")) %>% 
    mutate(Estimate_Rate_agg = paste(change_aggregate_rate, " (", round(aggregate_rate_lo_CI, 4), ", ", round(aggregate_rate_up_CI, 4), ")", sep = "")) %>% 
    mutate(Estimate_Count = paste(round(change_aggregate_count_annual, -3), " (", round(aggregate_lo_CI, -3), ", ", round(aggregate_up_CI,-3), ")", sep = ""))
```









